%% Example CV - Chuwei (Pete) Xu
%% Comprehensive overview of competencies, experience, and achievements.
%% Use as a master reference when tailoring role-specific CVs.
%% Compile with: lualatex main_example.tex

\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{blue}

% Force both first and last name AND section headings to render in moderncv
% blue (color1). Default banking on lualatex+MiKTeX leaves these black, which
% looks inconsistent with the rest of the blue accent scheme.
\renewcommand*{\firstnamestyle}[1]{{\fontsize{34}{36}\bfseries\upshape\color{color1}#1}}
\renewcommand*{\lastnamestyle}[1]{{\fontsize{34}{36}\bfseries\upshape\color{color1}#1}}
\renewcommand*{\sectionstyle}[1]{{\sectionfont\color{color1}#1}}

\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=blue,
    pdftitle={Chuwei Xu - CV},
    pdfpagemode=FullScreen,
}
\usepackage[scale=0.80]{geometry}
\usepackage{import}

% personal data
\name{Chuwei (Pete)}{Xu}
\address{New Jersey, United States}{}{}
\phone[mobile]{+1 (860) 634-1906}
\email{chuweismail@gmail.com}
\extrainfo{\href{https://linkedin.com/in/chuwei-xu}{LinkedIn}}

\begin{document}

\makecvtitle

% ============================================================
%     PROFILE STATEMENT
% ============================================================

\vspace{6pt}
\small{Software engineer with production experience building Java/Spring Boot microservices, Kafka-based post-trade processing pipelines, and OracleDB-backed trade lifecycle APIs in financial technology. Strong record of improving throughput, reliability, observability, and CI/CD delivery across enterprise environments.}

% ============================================================
%     CORE COMPETENCIES
% ============================================================

\section{Core Competencies}
\vspace{1pt}
\begin{itemize}

\item \textbf{Backend Engineering}: Java, Spring Boot, Spring Cloud, Spring Batch, Hibernate/JPA, microservices, REST APIs.

\item \textbf{Data and Messaging Systems}: Kafka, OracleDB, SQL, SQLite, Redis, XML parsing, ETL pipelines, data transform workflows.

\item \textbf{Production Reliability}: Elastic APM, Elasticsearch, distributed tracing, JVM metrics, alerting, validation retry logic, failure-rate monitoring.

\item \textbf{DevOps and Delivery}: GitLab CI/CD, Docker, OpenShift/Kubernetes, Jenkins, Ansible, Liquibase, TDD, regression testing.

\item \textbf{Web and Scripting}: Python, Django, Pandas, ElementTree, TypeScript, JavaScript (ES6+), React, Angular, C++.

\end{itemize}

% ============================================================
%     PROFESSIONAL EXPERIENCE
% ============================================================

\section{Professional Experience}
\vspace{3pt}
\begin{itemize}

\item{\cventry{Feb. 2023--Present}{Software Engineer}{Barclays}{New York, NY}{}{\vspace{1pt}
\begin{itemize}
    \item Engineered upstream high-throughput post-trade processing pipeline for FX and cash swap products across 7 Spring Boot microservices, improving daily trade event throughput on an internal Kafka streaming platform.
    \item Designed trade lifecycle APIs managing TradeStore ingestion, ATC enrichment, validation with automated retry logic, and OracleDB persistence using SQL Developer and Liquibase schema migrations.
    \item Architected distributed tracing with Elastic APM, achieving 100\% trace capture across a microservice chain and reducing cross-service investigation time by 40\%.
    \item Optimized end-of-day Kafka batch reconciliation by re-architecting sequential topic processing into parallel execution with Java CompletableFuture, reducing processing time from 60 minutes to 15 minutes for 5 primary topics.
    \item Established GitLab CI/CD infrastructure with static analysis, Docker builds, multi-stage pipelines, and automated OpenShift deployments across dev, SIT, UAT, and production.
\end{itemize}}}

\vspace{3pt}

\item{\cventry{Jun. 2022--Aug. 2022}{Software Engineer Intern}{Barclays}{New York, NY}{}{\vspace{1pt}
\begin{itemize}
    \item Implemented an ETL data processing tool for a risk management and data platform market team, improving elapsed time by 20\% through in-memory caching of parsed source data.
    \item Used Python ElementTree with Java, plus Anaconda Pandas, to improve data extraction and transform performance by 17\%.
    \item Scaled transform block implementation inside Ab Initio and contributed reusable error handling and testing blocks, increasing data cycle quality, accuracy, and scalability by 5\%.
\end{itemize}}}

\vspace{3pt}

\item{\cventry{Jan. 2022--May 2022}{Software Engineer Intern}{Cisco Systems, Inc.}{New York, NY}{}{\vspace{1pt}
\begin{itemize}
    \item Participated in Django backend construction for a hardware team, automating test-data detection and correction and increasing work efficiency by 68\%.
    \item Used Django and SQLite with watchdog and supervisor modules for background monitoring, error handling, and backend data-flow recording, reducing redundant labor by 55\%.
    \item Implemented structural framework design and deployed on Linux, improving output readability by 44\%.
\end{itemize}}}

\end{itemize}

% ============================================================
%     EDUCATION
% ============================================================

\section{Education}
\vspace{1pt}
\begin{itemize}

\item{\cventry{Sep. 2021--Dec. 2022}{M.S. in Industrial Engineering, Honors Scholar}{New York University}{New York, NY}{}{\vspace{1pt}
GPA: 3.6/4.0.
}}

\vspace{3pt}

\item{\cventry{Sep. 2017--May 2021}{B.S. in Mechanical Engineering, Honors Scholar}{New York University}{New York, NY}{}{\vspace{1pt}
GPA: 3.7/4.0.
}}

\end{itemize}

% ============================================================
%     HONORS AND AWARDS
% ============================================================

\section{Honors and Awards}
\vspace{1pt}
\begin{itemize}
\item{\textbf{Honors Scholar} -- New York University M.S. in Industrial Engineering.}
\item{\textbf{Honors Scholar} -- New York University B.S. in Mechanical Engineering.}
\end{itemize}

% ============================================================
%     REFERENCES
% ============================================================

\section{References}
\vspace{1pt}
\begin{itemize}
\item{Available upon request.}
\end{itemize}

\end{document}
